Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-01 paper/paper/SPIE/article.tex
WIP - timeseries prediction

What is missing is a rigorous, systematic, reproducible investigation of the *predictice* value of
RMT metrics across a wide variety of data, RMT analytic choices, choice of eigenfeature, and choice
of preprocessing. The current study aims to rectify this.

>>>>

In addition these issues stemming from ``research degrees of freedom'' (cite Gelman), there is also
a basic baseline comparison issue: RMT is mathematically non-trivial, the extraction of RMT
spectral statistics is computationally demanding, and eigenvalues, while easy to understand
mathematically, are difficult to interpret relative to simpler potential reductions of fMRI data.

What is missing is a rigorous, systematic, reproducible investigation of the *predictice* value of
RMT metrics across a wide variety of data, RMT analytic choices, choice of eigenfeature, and choice
of preprocessing, and for these RMT eigenfeatures to be compared to simpler alternative baselines.
The current study aims to do just this.
